A data-intensive assessment of the species-abundance distribution.

### 2015-04-09 defense_pres.tex
Reworks slides.

\section{Introduction}
\subsection{Let's begin with an example..}
\begin{frame}
\frametitle{Let's begin with an example...}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
\end{center}
\note{
\begin{itemize}
\item Many potential pattern-generating mechanisms.
\item Exhibits a hollow curve distribution.
\end{itemize}
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

\begin{frame}
\frametitle{Let's begin with an example...}
\begin{center}
\includegraphics[scale=.35]{./sad-data/dissertation/PatternProcess_example_text.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Patterns \& process.}
\begin{huge}
\begin{center}
Process\\ 
\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPatterns.png}\\
Pattern\\
\end{center}
\end{huge}
\end{frame}

@@

\section{Species abundance distribution comparisons}
\begin{frame}
\frametitle{SAD Comparisons}
\begin{large}
Most comparisons of the different models:
\end{large}
\begin{itemize}
\item Use only a small subset of available models (typically two).
\item Focus on a single ecosystem or taxonomic group
\item Fail to use the most appropriate statistical methods. 
\end{itemize}
\end{frame}

@@

\begin{frame}[t]{}
\frametitle{Acknowledgements}
Dr. Thomas Price \& USU Student Health Center.\\
~\\
Tea, heating pads, \& the Flint Hills of Kansas.\\
~\\
A very supportive husband \& family.\\
~\\
\begin{Large}
Publicly available data, \& the citizen scientists that make that possible.\\
\end{Large}
\end{frame}

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{This dissertation brought to you by:}
\begin{large}
Disability accommodations\\
\end{large}
Accessibility statement generator
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/trinket-access-generator.png}\\
https://trinket.io/python/2df3ea45cf
\end{center}
\note{
\begin{itemize}
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}}
\end{frame}

>>>>

\section{Introduction}
\subsection{Let's begin with an example..}
\begin{frame}
\frametitle{Let's begin with an example...}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/beetleabunds.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Let's begin with an example...}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/BeetleRAD.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Species abundance distribution}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
\end{center}
\note{
\begin{itemize}
\item Many potential pattern-generating mechanisms.
\item Exhibits a hollow curve distribution.
\end{itemize}
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

\begin{frame}
\frametitle{Pattern \& process.}
\begin{center}
\includegraphics[scale=.35]{./sad-data/dissertation/PatternProcess_example_text.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Patterns \& process.}
\begin{huge}
\begin{center}
Process\\ 
\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPattern.png}\\
Pattern\\
\end{center}
\end{huge}
\end{frame}

\begin{frame}[t]
\frametitle{Traditional approach}
\vspace{-7pt}
\begin{center}
\includegraphics[scale=.45]{./sad-data/dissertation/localclose.png}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{Broader approach}
\vspace{-7pt}
\begin{center}
\includegraphics[scale=.45]{./sad-data/dissertation/birdmapclose.png}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{Knowledge gaps}
\vspace{-7pt}
\begin{center}
\includegraphics[scale=.45]{./sad-data/dissertation/birdmap.png}
\end{center}
\end{frame}

@@

\section{Species abundance distribution comparisons}
\begin{frame}
\frametitle{SAD Comparisons}
\begin{large}
Most comparisons of the different models:
\end{large}
\begin{itemize}
\item Use a small subset of available models (typically two).
\item Focus on a single ecosystem or taxonomic group
\item Fail to use most appropriate statistical methods. 
\end{itemize}
\end{frame}

@@

\begin{frame}[t]{}
\frametitle{Acknowledgements}
Dr. Thomas Price \& USU Student Health Center.\\
~\\
A very supportive husband \& family.\\
~\\
\begin{Large}
Publicly available data, \& the citizen scientists that make that possible.\\
\end{Large}
\end{frame}

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{This dissertation brought to you by:}
\begin{large}
Disability accommodations\\
\end{large}
Tea, heating pads, \& the Flint Hills of Kansas.\\
Accessibility statement generator
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/trinket-access-generator.png}\\
https://trinket.io/python/2df3ea45cf
\end{center}
\note{
\begin{itemize}
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}}
\end{frame}
